\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{amsmath}

% Define custom colors
\definecolor{gnomyGreen}{HTML}{2F4F4F}
\definecolor{gnomyBrown}{HTML}{8B4513}
\definecolor{gnomyPlum}{HTML}{673147}
\definecolor{gnomyTeal}{HTML}{008080}
\definecolor{gnomyCream}{HTML}{F5F5DC}

% Section style
\titleformat{\section}
  {\normalfont\Large\bfseries\color{gnomyGreen}}
  {\thesection.}{0.5em}{}
\titlespacing{\section}{0pt}{*3}{*1}

% Subsection style
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{gnomyPlum}}
  {\thesubsection.}{0.5em}{}
\titlespacing{\subsection}{0pt}{*2}{*1}

% Answer box style
\newtcolorbox{answerbox}[1][]{colback=gnomyCream,colframe=gnomyGreen,
  boxrule=1pt,arc=4pt,width=\textwidth,boxsep=5pt,left=5pt,right=5pt,top=5pt,bottom=5pt,#1}

\begin{document}

% Header Block
{\centering
\color{gnomyBrown}\textbf{\Huge Gnomy Framework Reflection Questionnaire 1.0}\\[1em]
\color{gnomyGreen}\large Guided questions for deep reflection and insight within the Gnomy Framework\\
    \color{VictorianGrey}\large By Rickard V. Hultgren: Cultivating Emotional \& Strategic Clarity
    \vspace{0em} % Space after author line
\vspace{1em}
}

\begin{tcolorbox}[licensebox]
  \centering
  \textbf{Creative Commons Attribution 4.0 International License (CC BY 4.0)} \\
  This work, "TGnomy Framework Reflection Questionnaire 1.0: Cultivating Emotional \& Strategic Clarity," by Rickard V. Hultgren, is licensed under a Creative Commons Attribution 4.0 International License. To view a copy of this license, visit \url{http://creativecommons.org/licenses/by/4.0/}. \\
  \faIcon{creative-commons} \faIcon{creative-commons-by}
\end{tcolorbox}
}

% Step 0: Grounding
\section{Step 0: Grounding (FIND the LENS) --- Find Your Inner Position}

\subsection*{F – Feel your breath/urge}

\begin{itemize}[noitemsep]
  \item What urge or impulse do I notice in my body right now?
  \item What emotions are beneath this urge (e.g., anger, fear, excitement)?
  \item What urge might others involved be experiencing that is like or unlike mine?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\subsection*{I – Introduce pause}

\begin{itemize}[noitemsep]
  \item What else can I notice about my goals beyond the obvious ones?
  \item Which underlying or hidden goals might be influencing my reactions?
  \item What goals might others hold that I’m not fully aware of?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\subsection*{N – Notice urgency}

\begin{itemize}[noitemsep]
  \item Which goals feel most urgent or pressing for me and for others involved?
  \item What is one small constructive action I can take right now to address these goals?
  \item What aspects of the situation are beyond my control, and how can I accept that?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\subsection*{D – Discern Stakes (and Divine Compassion)}

\begin{itemize}[noitemsep]
  \item Who is experiencing the highest emotional stakes right now, and what emotions reveal this?
  \item Who faces the greatest physical vulnerability or potential harm here?
  \item What core values or sacred concerns feel threatened for those involved?
  \item How can I approach this understanding with deep compassion and humility for everyone?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\section*{Applying the LENS: Layered Emotive Narratives of Stakes}

\subsection*{L – Loss (Past) vs. Legitimacy (Past)}

\begin{itemize}[noitemsep]
  \item From my view: What past losses or harms do I perceive in this situation?
  \item From their view: What past actions do they believe were justified or deserving credit?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\subsection*{E – Effort (Present) vs. Entitlement (Present)}

\begin{itemize}[noitemsep]
  \item From my view: What current challenges am I facing, and what effort am I making?
  \item From their view: What actions do they see as justified, and why do they feel entitled?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\subsection*{N – Nuisance (Future) vs. Necessity (Future)}

\begin{itemize}[noitemsep]
  \item From my view: How might their future actions threaten or nuisance my goals?
  \item From their view: What future actions do they believe are necessary despite the impact on me?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\subsection*{S – Safety (My Goal) vs. Supremacy (Their Goal)}

\begin{itemize}[noitemsep]
  \item What is my ultimate goal for safety and well-being in this situation?
  \item What seems to be their ultimate goal for control, dominance, or supremacy?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

% Step 1: Narrative of Emotion and Meaning
\section{Step 1: Narrative of Emotion and Meaning}

\subsection*{1.1 Narrative (LUX) --- Explore Your Emotions and Their Roots}

\textbf{L – Longing}

\begin{itemize}[noitemsep]
  \item What desires or hopes am I secretly longing for in this situation?
  \item What “attractive features” or delights am I missing or feeling, and what emotions do they evoke?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{U – Usefulness}

\begin{itemize}[noitemsep]
  \item How does this situation affect my sense of control, competence, or well-being?
  \item What expected “performance features” are working or failing, and how does that make me feel?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{X – X-Friction}

\begin{itemize}[noitemsep]
  \item What specific threats, irritations, or pressures am I experiencing right now?
  \item Which basic needs or “must-be” features are unmet, causing frustration or anxiety?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\subsection*{1.2 Others (CROWS) — Who Else Is Part of This Emotional Story?}

\textbf{C – Current others}

\begin{itemize}[noitemsep]
  \item Who else is involved, and what might they be thinking or feeling right now?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{R – Retrospective self}

\begin{itemize}[noitemsep]
  \item How would my past self interpret or feel about this situation?
  \item What lessons from past challenges apply here?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\textbf{O – Optional future self}

\begin{itemize}[noitemsep]
  \item What emotional legacy do I want my future self to see from this moment?
  \item What advice might my wise future self offer?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\textbf{W – Wished-for others}

\begin{itemize}[noitemsep]
  \item Are there people whose opinions I value or wish to impress here?
  \item What kind of connection or impact do I want to have with them?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\textbf{S – Shared past}

\begin{itemize}[noitemsep]
  \item What shared histories or experiences influence this moment for those involved?
  \item How does our collective past shape current emotions and dynamics?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

% Step 2: Reframe Through Shared Competence and Action
\section{Step 2: Reframe Through Shared Competence and Action}

\subsection*{2.1 More (SPARK) --- Uncover Resources, Strengths, and Options}

\textbf{S – Strengths}

\begin{itemize}[noitemsep]
  \item What core strengths or positive qualities do I bring to this situation?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{P – Possibilities}

\begin{itemize}[noitemsep]
  \item What different paths or courses of action can I imagine, no matter how unconventional?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{A – Assets}

\begin{itemize}[noitemsep]
  \item What tangible and intangible resources do I have access to?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{R – Resourced Relationships}

\begin{itemize}[noitemsep]
  \item Who in my network can support or provide insight in this situation?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{K – Knowledge \& Experience}

\begin{itemize}[noitemsep]
  \item What relevant lessons, frameworks, or facts do I already possess to guide me?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\subsection*{2.2 Yikes! (SAGE) --- Face Risks, Limits, and Priorities}

\textbf{S – Spectrum}

\begin{itemize}[noitemsep]
  \item \textbf{Scary}: What is the worst-case outcome if I take action?
  \item \textbf{Sufficient}: What minimum outcome would be good enough to move forward?
  \item \textbf{Successful}: What would a meaningful win look like here?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\textbf{A – Actions}

\begin{itemize}[noitemsep]
  \item \textbf{Avoidance}: What might I be tempted to avoid or delay, and what happens if I do?
  \item \textbf{Anchoring}: What steady actions can keep me resilient through stress?
  \item \textbf{Aspiration}: What bold or values-aligned steps can I take toward success?
\end{itemize}
\begin{answerbox}
\vspace{4em}
\end{answerbox}

\textbf{G – Gauge}

\begin{itemize}[noitemsep]
  \item Which actions are most urgent and important right now?
  \item What is the immediate next step I can take?
\end{itemize}
\begin{answerbox}
\vspace{3em}
\end{answerbox}

\textbf{E – Evolution}

\begin{itemize}[noitemsep]
  \item \textbf{Examine}: What feedback or new information am I noticing from my actions?
  \item \textbf{Evaluate}: What parts of my plan work well, and which don’t?
  \item \textbf{Edit}: What must I adjust or let go of?
  \item \textbf{Expand}: What pain points have eased? What insights have I gained? Who was affected? How will I share these insights with others?
\end{itemize}
\begin{answerbox}
\vspace{5em}
\end{answerbox}

\end{document}
